---
title: "FAO_SlaugtherData"
author: "Adrian Hirt"
date: "`r Sys.Date()`"
output: 
  ioslides_presentation:
    widescreen: true
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(dplyr)
library(ggplot2)

```

## The Purpose

To visualize how the ratio of **animals slaughtered to inhabitants** has shifted globally from 1980-2018. 

## Why?
Animal agriculture sits at the intersection of some of the most pressing issues of our time. Intensive animal farming is a major factor in antimicrobial resistance, climate change and animal welfare. Particularly in developed countries the magnitude of the industry is often overlooked - this projects aims to visualize a broken system. 

## How?

The visualization will consist of two interactive world maps, presented as a shiny web application.  

1. The user will be able to select species and year. The map will be color-coded, indicating the country with the relative highest ratio in the given year. 
2. The user will be able to select a species and be presented with a color-coded world map, highlighting the countries with the most significant increase of slaughter numbers per capita.


## The Data

The data stems from [FAOSTAT](https://www.fao.org/faostat/en/#home), run by the Food and Agriculture Organization of the United Nations ([FAO](https://www.fao.org/home/en)).



```{r data, echo = TRUE}


```

## Slide with Plot

```{r pressure}
plot(pressure)
```

